Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Kerning

\begin{algorithm}[tb] \DontPrintSemicolon
\nl $\FuncSty{associationMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
\nl \Begin{
    \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \label{incumbent} \;
    \nl $G \gets G_1 \modularproduct G_2$ \label{buildassoc} \;
    \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \label{firstsearch} \;
    \nl $\KwSty{return} ~ \mathit{incumbent}$ \;
}
\vspace{1ex}
\nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
\nl \Begin{
    \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \label{makecolours} \;
    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{branchable}),$ \;
    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{branchable}))$ \;
    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$\label{outerloop}}{
        \nl \ForEach{$v \in \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$\label{innerloop}}{
            \nl \lIf{$|\mathit{solution}| + \FuncSty{length}(\mathit{colourClasses}) \leq
            |\mathit{incumbent}|$}{\KwSty{return}\label{bound}}
            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne
            \emptyset$}{\KwSty{return} \label{acceptbranchable}}
            \nl $\mathit{solution}' \gets \mathit{solution} \cup \{ v \} \label{addv} \label{addvtosolution} $\;
            \nl \lIf{$|\mathit{solution}'| > |\mathit{incumbent}|$}{$\mathit{incumbent} \gets
            \mathit{solution}'$ \label{newincumbent}}
            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \{ w \in G : \FuncSty{first}(w)
            \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \label{addtobranchable} \;
            \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \label{filterremaining} \;
            \nl \lIf{$\mathit{remaining}' \neq \emptyset$}{$\FuncSty{search}(G, \mathit{solution}',
            \mathit{branchable}', \mathit{remaining}')$\label{recursesearch}}
         }
         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
     }
}
\vspace{0.5ex}
\nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;
\nl \Begin{
    \nl $\KwSty{return}$ a greedy sequential colouring of the vertices in $\mathit{uncoloured}$,
    using the procedure of San Segundo et al.\ \cite{DBLP:journals/cor/SegundoRJ11} with a static
    degree order from $G$ and $k_{min} = 0$. \;
}
\caption{An algorithm for a maximum common connected induced subgraph isomorphism via an association graph.}
\label{algorithm:mccis}
\end{algorithm}

@@

Our $\FuncSty{colour}$ procedure is a simple greedy sequential colouring. We use the bit-parallel
algorithm introduced by San Segundo \textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}, with the
$k_{min}$ parameter set to $0$, so we do not present it here. We use a simple static degree
ordering; other initial vertex orderings have been considered on general clique problems
\cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}, and it is possible that
special properties of the association graph could be exploited in this step (for example, it is
always possible to colour the initial association graph using
$\operatorname{min}(\left|\operatorname{V}(G_1)\right|, \left|\operatorname{V}(G_2)\right|)$
colours, but with certain vertex orderings, a greedy sequential colouring will sometimes use
many more colours).

>>>>

\begin{algorithm}[tb] \DontPrintSemicolon
\nl $\FuncSty{associationMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
\nl \Begin{
    \nl $\KwSty{global} ~ \mathit{incumbent} \gets \emptyset$ \label{incumbent} \;
    \nl $G \gets G_1 \modularproduct G_2$ \label{buildassoc} \;
    \nl $\FuncSty{search}(G, \emptyset, \emptyset, \operatorname{V}(G))$ \label{firstsearch} \;
    \nl $\KwSty{return} ~ \mathit{incumbent}$ \;
}
\vspace{1ex}
\nl $\FuncSty{search}$ :: (Graph $G$, Set $\mathit{solution}$, Set $\mathit{branchable}$, Set $\mathit{remaining}$) \;
\nl \Begin{
    \nl $\mathit{colourClasses} \gets \FuncSty{concatenate}($ \label{makecolours} \;
    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \setminus \mathit{branchable}),$ \;
    $\hspace*{2em}\FuncSty{colour}(G, \mathit{remaining} \cap \mathit{branchable}))$ \;
    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$\label{outerloop}}{
        \nl \ForEach{$v \in \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$\label{innerloop}}{
            \nl \lIf{$|\mathit{solution}| + \FuncSty{length}(\mathit{colourClasses}) \leq
            |\mathit{incumbent}|$}{\KwSty{return}\label{bound}}
            \nl \lIf{$v \notin \mathit{branchable} ~ \KwSty{and} ~ \mathit{solution} \ne
            \emptyset$}{\KwSty{return} \label{acceptbranchable}}
            \nl $\mathit{solution}' \gets \mathit{solution} \cup \{ v \} \label{addv} \label{addvtosolution} $\;
            \nl \lIf{$|\mathit{solution}'| > |\mathit{incumbent}|$}{$\mathit{incumbent} \gets
            \mathit{solution}'$ \label{newincumbent}}
            \nl $\mathit{branchable}' \gets \mathit{branchable} \cup \{ w \in G : \FuncSty{first}(w)
            \in \operatorname{N}(G, \FuncSty{first}(v)) \}$ \label{addtobranchable} \;
            \nl $\mathit{remaining}' \gets \mathit{remaining} \cap \operatorname{N}(G, v)$ \label{filterremaining} \;
            \nl \lIf{$\mathit{remaining}' \neq \emptyset$}{$\FuncSty{search}(G, \mathit{solution}',
            \mathit{branchable}', \mathit{remaining}')$\label{recursesearch}}
         }
         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
     }
}
\vspace{0.5ex}
\nl $\FuncSty{colour}$ :: (Graph $G$, Set $\mathit{uncoloured}$) $\rightarrow$ List of List of Vertex \;
\nl \Begin{
    \nl $\KwSty{return}$ a greedy sequential colouring of the vertices in $\mathit{uncoloured}$,
    using the procedure of San Segundo et al.\ \cite{DBLP:journals/cor/SegundoRJ11} with a static
    degree order from $G$ and $k_{\mathit{min}} = 0$. \;
}
\caption{An algorithm for a maximum common connected induced subgraph isomorphism via an association graph.}
\label{algorithm:mccis}
\end{algorithm}

@@

Our $\FuncSty{colour}$ procedure is a simple greedy sequential colouring. We use the bit-parallel
algorithm introduced by San Segundo \textit{et al.}\ \cite{DBLP:journals/cor/SegundoRJ11}, with the
$k_{\mathit{min}}$ parameter set to $0$, so we do not present it here. We use a simple static degree
ordering; other initial vertex orderings have been considered on general clique problems
\cite{DBLP:journals/algorithms/Prosser12,DBLP:conf/lion/SegundoLB14}, and it is possible that
special properties of the association graph could be exploited in this step (for example, it is
always possible to colour the initial association graph using
$\operatorname{min}(\left|\operatorname{V}(G_1)\right|, \left|\operatorname{V}(G_2)\right|)$
colours, but with certain vertex orderings, a greedy sequential colouring will sometimes use
many more colours).
